\documentclass[a4paper,11pt]{article}
\usepackage[table]{xcolor}



\input{prelude}
\input{ldefs}
\newcommand{\highlight}[1]{\textcolor[rgb]{.0,0.0,1.0}{ #1}}

\usetikzlibrary{shapes,arrows}
\newcommand{\THESYSTEM}{\textsf{PsRB}}

% Define block styles
\tikzstyle{decision} = [diamond, draw, fill=blue!20, 
text width=4.5em, text badly centered, node distance=3cm, inner sep=0pt]
\tikzstyle{block} = [rectangle, draw, fill=blue!20, 
text width=5em, text centered, rounded corners, minimum height=4em]
\tikzstyle{line} = [draw, -latex']
\tikzstyle{cloud} = [draw, ellipse,fill=red!20, node distance=3cm,
minimum height=2em]

\begin{document}
\title{Path Sensitive Reachability Bound}

\author{}

\date{}

\maketitle
%
\begin{abstract}
    The number of times a given control location 
    inside a procedure is visited during the program execution.
    The upper bound on this execution number for 
    a given control location is referred to as the reachability-bound by~\cite{GulwaniZ10} in the first place.
    A tight reachability-bound
    can help to improve the analysis result on other program features.
    For example, in the resource cost analysis, this quantitative reachability property
    can help to provide a tighter
    bound on the resources consumed by a program such as time, memory,
    network traffic, power, etc.
    In the data analysis area,
    the reachability-bound on each program control location
    can help to improve the precision of the data training result. 
    In security, this reachability-bound helps to improve the accuracy
    in estimating the program's information leakage or uncertainty propagation, etc.
    However, computing a tight reachability-bound for a given program control location is challenging.
    Many works in the program analysis area develop algorithms estimating the program's loop bound or overall complexity.
    But there isn't a general analysis algorithm that
    computes the reachability-bound
    directly or path-sensitively.
    To leverage these limitations,
    we present a path-sensitive reachability-bound algorithm
    aiming to find a precise symbolic worst-case reachability-bound on the program's every control location in this paper.
    Our algorithm brings together two techniques:
    1. ranking function based amortized bound analysis through program abstraction, and
    2. loop summarization based multiple loop paths refinement
    and combines them effectively. 
    The effective combination improves the bound accuracy comparing to adopt either one of them.
    It allows us to compute precise reachability-bound on each program point path-sensitively.
    We implement a prototype and report on an experimental comparison with state-of-art tools over four different benchmarks.
\end{abstract}

\tableofcontents


\section{Introduction}
\label{sec:intro}
\input{introduction}
% %
\section{Overview}
\label{sec:overview}
\input{overview}
% %
\section{{Language and Program Model}}
\label{sec:language}
\input{language}
% %
\section{{The Reachability-bound}}
\label{sec:execution_rb}
\input{rb_definition}
% % 
\section{Main Steps of Path-sensitive Reachability-bound Analysis}
\label{sec:static_rb}
\input{alg-preface}
\section{Abstraction Transition Graph}
\label{sec:progabs}
\input{alg-progabs}
\section{Loop Refinement}
\label{sec:refine}
\input{alg-refine}
\section{Path-sensitive Reachability-bound Algorithm}
\label{sec:psrb}
\input{alg-psrb}
\section{Ranking Function Computation and Estimation}
\label{sec:rank}
\input{alg-rank}
\section{Loop Bound and Path Local Reachability-bound Computation}
\label{sec:pathlocalrb}
\input{alg-pathlocalrb}
\section{Loop Reachability-bound Computation}
\label{sec:looprb}
\input{alg-looprb}
% \section{Path and Program Point Reachability-bound Computation}
% \label{sec:alg-rb}
% \input{alg-rb}
\section{Path Reachability-bound Computation}
\label{sec:pathrb}
\input{alg-pathrb}

\section{Informal Discussion on the Path-sensitivity}
\label{sec:thminformal}
\input{alg-theorem_informal}
\section{Examples}
\label{sec:example}
\input{examples}
\section{Evaluation}
\label{sec:eval}
\input{eval}
\section{Related Work}
\label{sec:relatedwork}
\input{relatedwork}
%
\section{Conclusion and Future Works}
\label{sec:conlusion}
\input{conclusion}
\clearpage


\bibliographystyle{plain}
\bibliography{main.bib}
\clearpage

\appendix
\addcontentsline{toc}{section}{Appendices}
\section*{Appendices}
\input{appendix}

\end{document}



