\begin{lemma}[Soundness of the Loop Reachability-Bound]
    For any loop $l: \rprog$ and a simple transition path $\tpath$ in a refined program, if $l':\rprog'$ is the closest loop enclosing the $\tpath$, then the entering times of $l':\rprog'$ when executing the $l: \rprog$, is bounded by $\lpchB(l: \rprog, \tpath)$.
  \end{lemma}
  \begin{proof}
    \emph{Loop Reachability-Bound} Soundness.
    \\
$\lpchB(l: \rprog, \tpath) \in \mathcal{A}_{\lin}$ 
Taking an arbitrary program $c$, let $\rprog$ be its refined program and $\tpath$ be an arbitrary transition path in this program.
\\
Let $l_t: \rprog_t = \kw{enclosed}(\rprog, \tpath)$ be the closest loop program where $\tpath$ is nested
and $l: \rprog_l \in \rprog$ be any loop in this program where $\tpath$ is nested.
\\
Let $\trace_0 \in \tdom_0(c)$ be an arbitrary initial trace.
\\
To show that $\lpchB(l: \rprog_l, \tpath)$ bounds the iteration numbers of the loop $l$ w.r.t.
the inner loop $l_t: \rprog_t$ 
such that during the iterations of loop $l$, the nested loop $l_t: \rprog_t$ is executed,
by Definition~\ref{def:looprb}, we have
\[
    \lpchB(l: \rprog_l, \tpath) \triangleq
    \frac{\lpinit(l: \rprog, \tpath) - \rffinal(\tpath)}{\lpnext(l: \rprog, \tpath)}.
\]
The soundness is guaranteed by the operation
 $\frac{\lpinit(\rprog, \tpath) - \rffinal(\rprog, \tpath)}{\lpnext(\rprog, \tpath)}$ and the three states,
 $\lpinit(\rprog, \tpath)$, $\rffinal(\rprog, \tpath)$, $\lpnext(\rprog, \tpath)$ computed in Definition~\ref{def:alg-loopabsstate}
 as follows.
\begin{itemize}
  \item \emph{Loop Initial State} Soundness.
    By Definition~\ref{def:alg-loopabsstate}, we have $\lpinit(\rprog, \tpath)$ 
    \[
      \lpinit(l: \rprog, \tpath) \triangleq 
      \arg\max_{l_1}\left\{
          \varinvar(y) + v ~\middle\vert~ 
          \begin{array}{l} 
            (l_1, x' \leq y + v, l_2) \in \reset(x) 
            \\
            \land \absinit(\rprog) \leq l_1 \leq \absinit(\tpath)
          \end{array}
        \right\}, x = \locbound(\tpath)
      \]
  By the soundness of the rank estimation in Lemma~\ref{lem:local_bound_sound} and Theorem~\ref{thm:pathinsensitive_rb_soundness}, we know $\varinvar(\locbound(\tpath))$ is a sound upper bound on $\tpath$'s ranking function,
  and $\varinvar(y)$ is also sound upper bound on all the variables that reset $\locbound(\tpath)$.
  \\
  In this sense, we have $\arg\max_{l_1}\left\{
    \varinvar(y) + v ~\middle\vert~ 
    \begin{array}{l} 
      (l_1, x' \leq y + v, l_2) \in \reset(x) 
      \\
      \land \absinit(\rprog) \leq l_1 \leq \absinit(\tpath)
    \end{array}
  \right\}, x = \locbound(\tpath)$
  is a sound initial value estimation of $\locbound(\tpath)$.
  %
  \item $\rffinal(\tpath)$ computes the value of $\locbound(\tpath)$ after the iteration of $l_t:\rprog_t$ finished.
  In this sense, $\rffinal(\tpath)$ is the correct value of $\locbound(\tpath)$ after the first execution of $l_t:\rprog_t$.
  %
  \item  $\lpnext(\rprog, \tpath)$ computes the variables states of the $\tpath$
  after visited the program point $l$ the second time and before visiting any other program point.
  In the same time, the soundness also relies on an external solver. 
\end{itemize}
By the soundness of the three states above, we know $\frac{\lpinit(\rprog, \tpath) - \rffinal(\rprog, \tpath)}{\lpnext(\rprog, \tpath)}$ soundly computes the maximum number of $l: \rprog_l$'s iteration times such that during these iterations, the nested loop $l_t: \rprog_t$ is executed.
\end{proof}