\begin{lemma}[Soundness of the Path Local Reachability-Bound]
    For any refined program $\rprog$ and a simple transition path $\tpath$ in this program,
    if $l: \rprog_l = \kw{enclosed}(\rprog, \tpath)$ is the closest loop where $\tpath$ is nested,
    then the execution times of $\tpath$ when executing the $\rprog_l$ is bounded by $\outinB(\rprog_l, \tpath)$.
  \end{lemma}
\begin{proof}
\emph{Path Local Reachability-Bound} Soundness.
\\
Taking an arbitrary program $c$, let $\rprog$ be its refined program and $\tpath$ be an arbitrary transition path in this program.
\\
Let $l: \rprog_l = \kw{enclosed}(\rprog, \tpath)$ be the closest loop program where $\tpath$ is nested.
\\
Let $\trace_0 \in \tdom_0(c)$ be an arbitrary initial trace.
\\
To show $\outinB(\rprog_l, \tpath) \geq \counter(\trace, L(\tpath))$, by induction on the loop program $\rprog_l$,
we have the following cases:
\caseL{$\rprog_l = \tpath$}
$\outinB(\tpath, \tpath) = 1$
\caseL{$\rprog_l = \tpath'$}
$\outinB(\tpath', \tpath) = \highlight{0} $
\caseL{$\rprog_l = \rprog_1;\rprog_2$}
$\outinB(\rprog_1;\rprog_2, \tpath) = \outinB(\rprog_1, \tpath) + \outinB(\rprog_2, \tpath) $
\caseL{$\rprog_l = \rpchoose{\rprog_1, \ldots, \rprog_m }$}
$\outinB(\rpchoose{\rprog_1, \ldots, \rprog_m }, \tpath) = \max\left\{ \outinB(\rprog_1, \tpath), \ldots, \outinB(\rprog_m, \tpath) \right\}$ 
Sound by induction hypothesis and the $\max$ operation.
\caseL{$\rprog_l = \rprepeat(\rprog')$ }
$\outinB(\rprepeat(\rprog'), \tpath) = BD(\rprepeat(\rprog')) \times \outinB(\rprog', \tpath)$
For a simple transition path $\tpath$ only enclosed by one transition path $\rprepeat(\tpath)$, 
we know $\outinB(\rprog, \tpath) = \outinB(\rprepeat(\tpath), \rprog)$.
Since $\outinB(\rprepeat(\tpath), \rprog)$ is a sound local bound on the iteration times
of $\rprepeat(\tpath)$ by assuming all the outside loops executes only once.
In this sense, $\outinB(\rprepeat(\tpath), \rprog)$ is also a sound bound on the iteration times globally.
\\
For a simple transition path $\tpath$ nested in multiple transition paths $\rprog_1, \ldots, \rprog_m$,
we know $\outinB(\rprog, \tpath) = \prod\limits_{i = 1, \ldots, m}\outinB(\rprog_i, \rprog)$.
By the same guarantee from $\outinB(\rprog_i, \rprog)$, it is sound to multiply each of them.
\caseL{$\rprog_l = l': \rprog'$}
$\outinB(l': \rprog', \tpath) = \outinB(\rprog', \tpath)$ 
\text{this case always equals to } 0 because $\rprog_l$ is the enclosed loop where $\tpath$ is nested, and there doesn't exist two different $\kw{enclosed}(\rprog, \tpath)$.

\end{proof}