%% For double-blind review submission, w/o CCS and ACM Reference (max submission space)
\documentclass[sigplan,10pt,review,anonymous]{acmart}
\settopmatter{printfolios=true,printccs=false,printacmref=false}
%% For double-blind review submission, w/ CCS and ACM Reference
%\documentclass[sigplan,review,anonymous]{acmart}\settopmatter{printfolios=true}
%% For single-blind review submission, w/o CCS and ACM Reference (max submission space)
%\documentclass[sigplan,review]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
%% For single-blind review submission, w/ CCS and ACM Reference
%\documentclass[sigplan,review]{acmart}\settopmatter{printfolios=true}
%% For final camera-ready submission, w/ required CCS and ACM Reference
%\documentclass[sigplan]{acmart}\settopmatter{}

% \input{prelude}
% \input{ldefs}
% \newcommand{\highlight}[1]{\textcolor[rgb]{.0,0.0,1.0}{ #1}}

%% Conference information
%% Supplied to authors by publisher for camera-ready submission;
%% use defaults for review submission.
\acmConference[PL'18]{ACM SIGPLAN Conference on Programming Languages}{January 01--03, 2018}{New York, NY, USA}
\acmYear{2018}
\acmISBN{} % \acmISBN{978-x-xxxx-xxxx-x/YY/MM}
\acmDOI{} % \acmDOI{10.1145/nnnnnnn.nnnnnnn}
\startPage{1}

%% Copyright information
%% Supplied to authors (based on authors' rights management selection;
%% see authors.acm.org) by publisher for camera-ready submission;
%% use 'none' for review submission.
\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\copyrightyear{2018}           %% If different from \acmYear

%% Bibliography style
\bibliographystyle{ACM-Reference-Format}
%% Citation style
%\citestyle{acmauthoryear}  %% For author/year citations
%\citestyle{acmnumeric}     %% For numeric citations
%\setcitestyle{nosort}      %% With 'acmnumeric', to disable automatic
                            %% sorting of references within a single citation;
                            %% e.g., \cite{Smith99,Carpenter05,Baker12}
                            %% rendered as [14,5,2] rather than [2,5,14].
%\setcitesyle{nocompress}   %% With 'acmnumeric', to disable automatic
                            %% compression of sequential references within a
                            %% single citation;
                            %% e.g., \cite{Baker12,Baker14,Baker16}
                            %% rendered as [2,3,4] rather than [2-4].


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Note: Authors migrating a paper from traditional SIGPLAN
%% proceedings format to PACMPL format must update the
%% '\documentclass' and topmatter commands above; see
%% 'acmart-pacmpl-template.tex'.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%% Some recommended packages.
\usepackage{booktabs}   %% For formal tables:
                        %% http://ctan.org/pkg/booktabs
\usepackage{subcaption} %% For complex figures with subfigures/subcaptions
                        %% http://ctan.org/pkg/subcaption

\input{prelude}
\input{ldefs}
\newcommand{\highlight}[1]{\textcolor[rgb]{.0,0.0,1.0}{ #1}}
\usetikzlibrary{shapes,arrows}
\newcommand{\THESYSTEM}{\textsf{PsRB}}
                        
\begin{document}

%% Title information
\title[Short Title]{Path Sensitive Reachability Bound Analysis}         %% [Short Title] is optional;
                                        %% when present, will be used in
                                        %% header instead of Full Title.
\titlenote{with title note}             %% \titlenote is optional;
                                        %% can be repeated if necessary;
                                        %% contents suppressed with 'anonymous'
\subtitle{Subtitle}                     %% \subtitle is optional
\subtitlenote{with subtitle note}       %% \subtitlenote is optional;
                                        %% can be repeated if necessary;
                                        %% contents suppressed with 'anonymous'


%% Author information
%% Contents and number of authors suppressed with 'anonymous'.
%% Each author should be introduced by \author, followed by
%% \authornote (optional), \orcid (optional), \affiliation, and
%% \email.
%% An author may have multiple affiliations and/or emails; repeat the
%% appropriate command.
%% Many elements are not rendered, but should be provided for metadata
%% extraction tools.

%% Author with single affiliation.
\author{First1 Last1}
\authornote{with author1 note}          %% \authornote is optional;
                                        %% can be repeated if necessary
\orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
\affiliation{
  \position{Position1}
  \department{Department1}              %% \department is recommended
  \institution{Institution1}            %% \institution is required
  \streetaddress{Street1 Address1}
  \city{City1}
  \state{State1}
  \postcode{Post-Code1}
  \country{Country1}                    %% \country is recommended
}
\email{first1.last1@inst1.edu}          %% \email is recommended

%% Author with two affiliations and emails.
\author{First2 Last2}
\authornote{with author2 note}          %% \authornote is optional;
                                        %% can be repeated if necessary
\orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
\affiliation{
  \position{Position2a}
  \department{Department2a}             %% \department is recommended
  \institution{Institution2a}           %% \institution is required
  \streetaddress{Street2a Address2a}
  \city{City2a}
  \state{State2a}
  \postcode{Post-Code2a}
  \country{Country2a}                   %% \country is recommended
}
\email{first2.last2@inst2a.com}         %% \email is recommended
\affiliation{
  \position{Position2b}
  \department{Department2b}             %% \department is recommended
  \institution{Institution2b}           %% \institution is required
  \streetaddress{Street3b Address2b}
  \city{City2b}
  \state{State2b}
  \postcode{Post-Code2b}
  \country{Country2b}                   %% \country is recommended
}
\email{first2.last2@inst2b.org}         %% \email is recommended


%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
Goal: bound the number of visiting times for every program control location, i.e., Solve the 
\emph{Reachability-Bound Program}.
Motivation: State-of-Art Techniques 
\\
in paper~\cite{Sumit2010rechability,sinn2017complexity} : path-insensitive 
\\
in paper~\cite{GulwaniJK09} : path-sensitive and precise for estimating loop bounds, but over-approximate reachability times of control location with loop bound.
\\
in paper~\cite{ZulegerGSV11} : able to identify different paths from multiple-path loop, but aims to solve bounds for loop and path. They over-approximate reachability times of control location with loop bound.
\\
Contribution: 
Solve the 
\emph{Reachability-Bound Program} precisely /(improve accuracy),  in two challenging classes of programs: Program with Path-Sensitive Loops, and Program with Nested Loops 
\\
improve efficiency by abstracting program using the Difference Constraint-base method in \cite{sinn2017complexity}.
\\
Implementation.
\end{abstract}


%% 2012 ACM Computing Classification System (CSS) concepts
%% Generate at 'http://dl.acm.org/ccs/ccs.cfm'.
\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10011007.10011006.10011008</concept_id>
<concept_desc>Software and its engineering~General programming languages</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10003456.10003457.10003521.10003525</concept_id>
<concept_desc>Social and professional topics~History of programming languages</concept_desc>
<concept_significance>300</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Software and its engineering~General programming languages}
\ccsdesc[300]{Social and professional topics~History of programming languages}
%% End of generated code


%% Keywords
%% comma separated list
\keywords{keyword1, keyword2, keyword3}  %% \keywords are mandatory in final camera-ready submission


%% \maketitle
%% Note: \maketitle command must come after title commands, author
%% commands, abstract environment, Computing Classification System
%% environment and commands, and keywords command.
\maketitle


\section{Introduction}
\label{sec:intro}
\input{introduction}
\section{Overview}
\label{sec:overview}
\input{overview}
\section{{Program Model}}
\label{sec:language}
\subsection{Language}
\subsection{Trace-Based Operational Semantics}
% \input{language}
% %
% %
\subsection{{Reachability Bound Formalization}}
\label{sec:execution_rb}
% \input{execution_reachabilitybound}
% % 
\section{Path Sensitive Reachability Bound Analysis}
\label{sec:static_rb}
% \input{static_reachabilitybound}
% % % % 
\subsection{Constraint Program}
Constraint program is a directed labeled transition graph,
\\
Label: Difference Constraint $\cup$ Set of Boolean Expressions.
\\
Generating Steps: 
\\
Constraint Event : 1 edge of the Constraint Program, and 
\\
Constraint Execution Trace : the edge set of the Constraint Program.
\\
Soundness and Uniqueness.
\\
"Expressions"
\subsection{Constraint Program Refinement}
Algorithm Steps:
\\
Simple Transition Path from Constraint Program: "Path" with at most one simple loop.
\\
Choose annotation for two branches of if.
\\
Loop annotation for body of while.
\\
Refine the loop body by algorithm in \cite{GulwaniJK09}.
%
\subsection{Outside-In Algorithm}
\label{sec:outsidein}
Main Algorithm:
\\
Computation Operators Required by algorithm:
\\
Variable Constraint Collection:
\\
Initial Constraint State:
\\
=> Require Variable Resets.
\\
Final Constraint State:
\\
 => Require Variable Bound Computation.
\\
Variable Grade Decedent:
\\
 => Require Variable Decs and Incs.
\\
Operators Computation Details:
\\
Alternative/Equivalent Computation method from paper \cite{GulwaniJK09}.
\subsection{Inside-Out Algorithm}
\label{sec:insideout}
Main Algorithm Steps:
\\
1. Local Repeat Chain Bound :
\\
=> Require : Repeat chain and Result from~\ref{sec:outsidein}.
\\
=> Compute : path sensitive local bound for every "Simple Transition Path", inside its closet while loop.
\\
2. Nested Loop Bound:
\\
=> Require : Loop Chain and Result from~\ref{sec:outsidein} and Step 1 above.
\\
=> Compute : For every "Simple Transition Path" the path-sensitive
reachability bound for the number of the "Outside-Loop"'s execution iterations
%  will 
such that, during these iterations, the "Simple Transition Path" will be executed. 
\\
3. Global Loop Bound.
\\
=> Require : Result from~\ref{sec:outsidein}, Step 1 and Step 2 above.
\\
=> Compute : path sensitive reachability bound for every "Simple Transition Path".
%
\subsection{Path Sensitive Reachability Bound Computation}
=> Require : Result from~\ref{sec:outsidein} and \ref{sec:insideout}.
\\
=> Compute : path sensitive reachability bound for every execution location (i.e., label).
\section{Examples and Experimental Results}
\label{sec:example}


%% Acknowledgments
\begin{acks}                            
  %% acks environment is optional
  %% contents suppressed with 'anonymous'
%% Commands \grantsponsor{<sponsorID>}{<name>}{<url>} and
%% \grantnum[<url>]{<sponsorID>}{<number>} should be used to
%% acknowledge financial support and will be used by metadata
%% extraction tools.
This material is based upon work supported by the
\grantsponsor{GS100000001}{National Science
Foundation}{http://dx.doi.org/10.13039/100000001} under Grant
No.~\grantnum{GS100000001}{nnnnnnn} and Grant
No.~\grantnum{GS100000001}{mmmmmmm}.  Any opinions, findings, and
conclusions or recommendations expressed in this material are those
of the author and do not necessarily reflect the views of the
National Science Foundation.
\end{acks}

%% Bibliography
%\bibliography{bibfile}
\bibliography{main.bib}

%% Appendix
\appendix
\section{Appendix}
\subsection{Program Model Properties}
\label{apdx:lemma_sec123}
% \input{theorem/lem_section123}

\subsection{Soundness of Path-Insensitive Reachability Bounds Estimation}
\label{apdx:pathinsensitive_rb_soundness}
% \input{theorem/pathinsensitive_rb_soundness}

\subsection{Soundness of Path-Sensitive Reachability Bounds Estimation}
\label{apdx:pathsensitive_rb_soundness}

\end{document}
