In this section, we discuss a running example we took from
the benchmark set of~\cite{GulwaniZ10} with
challenges of computing the symbolic
\emph{reachability-bound} on
every control location. Then we illustrate how our algorithm leverages the challenges through the \emph{path reachability-bound} and the \emph{loop reachability-bound}.

\input{examples/relatedNestedWhileOdd-overview}

\textbf{Challenge I}
The example program in Figure~\ref{fig:relatedNestedWhileOdd-overview}(a) has two level nested loops, outer loop $L_1$ and nested loop $L_4$ which is in the first path of $L_1$. Given $n \geq m \geq 0$,
the expected \emph{reachability-bound}s for locations in outer loop $3, 6, 7$ and $8$ are all $\lfloor\frac{m}{4}\rfloor$,
% for $8$ is $\lfloor\frac{m}{4}\rfloor + 1$,
for location $2$ is $\lfloor\frac{m}{2}\rfloor$ and $\lfloor\frac{m}{2}\rfloor + 1$ for location $1$.
{Though within the same loop $L_1$, the bounds for different locations are different.}
Amortized analysis tools such as Loopus~\cite{SinnZV17}, KoAT~\cite{BrockschmidtEFFG14,FalkeKS12,FalkeKS11}, C4B~\cite{CarbonneauxHS15}, etc. ignore path sensitivity and approximate the bound $n$ as the bound for loop $L_1$. 
While some path-refinement-based methods such as \cite{GulwaniZ10,GulwaniJK09}, CoFloCo~\cite{Montoya17,Flores-Montoya16,Flores-MontoyaH14} and etc. give the same bound for all the locations within the loop $L_1$. 
Although we can reuse their results i.e., loop bounds as the \emph{reachability-bound} for location $1$ and $2$,
it is still unclear for locations $3, 6, 7$, and $8$.
%
This motivates our first key novelty -- the \emph{path reachability-bound}
for a loop-free and interleaving-free path $\tpath$.
It bounds the times that each path is evaluated in a path-refined program.

\textbf{Challenge II} T
\highlight{he second challenge occurs in the nested loop.
In the command of label 3, $k$ is reset by $i - m$, and $i$ is reset by $k + m$ after the
loop $L_4$, so $L_4$ is only executed in the first iteration of loop $L_1$.
We say the loop $L_4$ is ``reached'' only once in the outer loop $L_1$.
% \\
The total number of loop iterations is
$n - m + \lfloor\frac{m}{2}\rfloor + 1$,
and the tight \emph{reachability-bound} for location $5$ inside $L_4$ is $m$, which is the same as this innermost loop iteration bound.
% \\
}
Existing approaches either ignore path sensitivity or compute the same bound for all the locations in a loop.
None of them can give the precise \emph{reachability-bound}s for different locations in the loop.
Even if the loop bound is known, they are non-trivial to compute.
This motivates us to consider our second novel quantity --
the numbers of iterations of the {outer loop $L_1$} such that,
during these iterations, the loop $L_4$ is ``entered'', which is expected to be $1$. 
We refer to this quantity as the \emph{loop reachability} of the inner loop $L_4$ w.r.t the outer loop $L_1$.
% of the location within loop $L_6$ w.r.t the loops $L_3$ and $L_1$.
By multiplying the \emph{path reachability-bound} of $\tpath_3$ within $L_4$
with its \emph{loop reachability-bound} w.r.t $L_1$, we can obtain an accurate
\emph{reachability-bound} for location $5$.
% This quantity isn't considered or computed in any of the previous works.
\cite{GulwaniJK09} considers a similar quantity using the \emph{Progress Invariant}, but it bounds the iteration times of {inner loop $L_4$} w.r.t. one iteration of $L_1$, which is $m$. They still over-approximate the bound for locations inside $L_4$ as $m \times (n - m)$.
With these two key quantities, our algorithm computes the reachability-bound for this example through the following steps.
