% \subsection{Cost Analysis}

\paragraph*{Program Abstraction.}
The program abstraction techniques are widely used in program analysis area to precisely summarize the key property of the program.
In analyzing the loop bounds, the unified lattice model~\cite{CousotH78}, polyhedra~\cite{CousotC77} and octagons~\cite{Mine06} are used in~\cite{GulwaniZ10} for summarize the loop transition and generating the transition system.
But none of the three abstraction models can represent the if guard in multipath loop, and solving the transition system using these abstraction models is low-efficient.
The wedge abstract developed in~\cite{KincaidCBR18} for generating the non-linear loop invariant
computing the reachability-bound can also be used. While it only works well for the specific targeting problem, and still low-efficient or inaccuracy in summarizing the multipath loops and solving the path-sensitive reachability-bound problem. 
Compare to them, we choose to use the difference constrain based program abstraction model combined with boolean expression abstraction to generate our abstract transition graph. It can represent the program loops path-sensitively more is more accurate than the state-of-art program abstraction models mentioned above.
While our program abstraction model is based on the difference constrain model in~\cite{SinnZV17} and the size change abstraction in~\cite{SinnZV14}, which is more efficient comparing to the models above. The efficiency also benefit from our
semantics model, which is inspired from~\cite{Cousot19a} and~\cite{Cousot19} and has similar intuition with the program model in~\cite{SinnZV17}.

% \paragraph{Type-Based Static Cost Analysis.}
\paragraph{Program Cost Analysis.}
As already introduced in the introduction section, many works in cost analysis area focus on analyzing the loop iteration bound.
Though our motivation is mainly inspired from the SPEED tool in paper~\cite{GulwaniZ10}, they only infer overall loop bounds path-insensitively.
We also implement part of the algorithm in Loopus based on~\cite{SinnZV17} in terms of program abstraction and variable invariant generation,
and the path refinement algorithm from paper~\cite{GulwaniJK09}, but both of them suffer from the same weakness as~\cite{GulwaniZ10}.
The works in analyzing the program complexity~\cite{GustafssonEL05,HumenbergerJK18} only focus on estimating 
the overall complexity 
by inferring the bounds on the loop iteration numbers.
Similarly, the algorithm of computing a program's worst-case resource cost
such as~\cite{AlbertAGP08,AliasDFG10} reason the worst-case running time and resource cost of the program's entire execution as well.
For the same reason, the tools CofloCo~\cite{Montoya17,Flores-MontoyaH14,Flores-Montoya16}, KoAT~\cite{BrockschmidtEFFG16,BrockschmidtEFFG14,FalkeKS12,FalkeKS11}, and the amortized algorithm in~\cite{LuCT21} which we evaluated over our benchmarks all give only the entire loop bound path-insensitively.

\cite{CraryW00} presents a type system for the certification of resource bounds (once they are provided by the programmer). In contrast, we infer bounds for different program location. 
\cite{JostHLH10} uses linear programming to infer bounds for functional programs, but they are restricted to computing only linear bounds.
Other techniques that are based on
type system~\cite{CicekBG0H17,RajaniG0021}, the cost analysis via effect systems~\cite{CicekBG0H17,RadicekBG0Z18,QuG019}, and Hoare logic~\cite{CarbonneauxHS15}
give the approximated upper bound of the program's total resource cost as well but still failed to consider the path sensitivity and the resource cost on different program points.

\paragraph{Loop Summarization and Termination Analysis.}
There are numerous works studying the loop termination, 
invariant generation. Algorithms and techniques in this area are closely related to the bound analysis and loop path refinement.
For example, the termination analysis through ranking functions originated from paper~\cite{BradleyMS05} and followed up papers~\cite{FalkeKS11,FalkeKS12,CookSZ13,Zuleger18} are widely developed into bound analysis~\cite{AliasDFG10,SinnZV14,BrockschmidtEFFG16,BrockschmidtEFFG14}.
Loop summarization and invariant generate through path refinement~\cite{ManoliosV06,BalakrishnanSIG09,SharmaDDA11,Flores-MontoyaH14,HumenbergerJK18,CyphertBKR19} techniques are also extended into precise resource cost and loop bound estimation based on multiple loop path refinement~\cite{GulwaniJK09,ZulegerGSV11}. 
% Invariant Generation Through Ranking functions~\cite{AliasDFG10} for multipath loops.
Paper \cite{KincaidBCR19} introduce a precise closed-form loop summarization techniques which can help to improve the accuracy of the path refinement, as well as the non-linear loop summarization techniques~\cite{KincaidCBR18} and the invariant generating algorithm considering recurrence in~\cite{BreckCKR20}. They are all heavy compare to our light-weight path refinement implementation adapted from~\cite{GulwaniJK09}.
% \cite{CyphertBKR19} introduced a precise path refinement techniques over regular expression. While it is accurate only for loop summarizing and invariant generating under the specific recurrence loop program, and doesn't work well in multipath loop refinement.
The contextualization path refinement algorithm, based on the loop termination techniques in~\cite{ManoliosV06} are used in both~\cite{ZulegerGSV11,SinnZV14}. While this refinement only computes the multiple paths interleaving for one iteration, which is loose comparing to our path refinement implementation limited to at most $100$ iterations.



\section{Related Work.}
% \begin{itemize}
% \item 
\emph{Program Abstraction.}
Program abstraction is commonly used in program analysis as a preprocessing step to abstract program features and generates transition graphs or systems. For example, Gulwani et al.~\cite{GulwaniZ10} summarizes programs into some underlying abstract domains (the unified lattice~\cite{CousotH78}, polyhedra~\cite{CousotC77} or octagonal~\cite{Mine06})
and generates transition systems for loop counters. Kincaid et al.~\cite{KincaidCBR18} abstract  programs into the wedge domain and compute non-linear loop invariant.
% While it only works well for the specific targeting problem.
%Efficiency is the main bottleneck when generating and solving the constraint.
Sinn et al.~\cite{SinnZV17,SinnZV14}
introduce a program abstraction model based on difference constraints, which we also use in this paper. 
It is more accurate in the sense that it allow to represent program loops in a path-sensitive way.
 This representation is also comparatively lightweight.

% \item 
\emph{Amortized Complexity Analysis.}
This line of work follows 
% \emph{amortized complexity analysis}
% originated 
from Tarjan's seminal paper~\cite{Tarjan85}. It is usually combined with ranking functions~\cite{BradleyMS05,CookSZ13,Zuleger18} or counter increments~\cite{GulwaniMC09,ZulegerGSV11,AliasDFG10}.
% They do well in nested loops by alternating the loop bound computation with the ranking or counter estimation. This alternation is efficient without recursively unrolling the nested loops when composing the bound of different paths.
 % \\
 Techniques that estimate the counter increments or the ranking function invariants, such as the tools CofloCo~\cite{Montoya17,Flores-MontoyaH14,Flores-Montoya16} and KoAT~\cite{BrockschmidtEFFG16,BrockschmidtEFFG14,FalkeKS12,FalkeKS11}, or the algorithm in~\cite{LuCT21}, often ignore the interleaving between multiple paths in the same loop, on which we focus in this paper.
% Most of them 
%and etc.
% over-approximate the loop bound when the path interleaving affects loop execution.
%It is hard to repurpose their result as the reachability-bound on different points.
% loop bound path-insensitively as the reachability-bound on different points.
Several works have studied \emph{amortized complexity analysis} using type refinement and annotations~\cite{CraryW00,JostHLH10,CicekBG0H17,RajaniG0021,CarbonneauxHS15}. Most of these work also do not distinguish different paths in loops, resulting in over-approximation of the resource cost for different program points.
% We choose to use difference-constraints based approach and enrich it with boolean expressions and path-sensitivity according to the Alg.~2 in~\cite{SinnZV14},
% which assigns a variable to each edge on which this variable decrease as its ranking function.
% the Alg.~3 in~\cite{ZulegerGSV11},
% and the Def.~25 in Section 4 from~\cite{SinnZV17}.

\emph{Path Refinement Based Complexity Analysis}.
Another line of related works aims at analyzing loop bounds through loop summarization and path refinements~\cite{ManoliosV06,BalakrishnanSIG09,SharmaDDA11,Flores-MontoyaH14,HumenbergerJK18,CyphertBKR19}, and some of them also analyze the interleaving between different paths~\cite{GulwaniJK09,ZulegerGSV11}.
Kincaid et al.\cite{KincaidBCR19,KincaidCBR18,BreckCKR20} introduce some loop summarization techniques which can help to improve the accuracy of the path refinement algorithm for non-linear loops and with program recurrence.
% summarization techniques~\cite{KincaidCBR18} and the invariant generating algorithm considering recurrence in~\cite{BreckCKR20}. 
However, when composing the bound in nested loops, recursively unrolling the nested loops is heavy and in most cases non-terminating.
%
In contrast, our method simplifies the path refinement algorithm in~\cite{GulwaniJK09} using contextualization techniques based on~\cite{ZulegerGSV11,SinnZV14,ManoliosV06}.
We also limit the iterations of the refinement algorithm to a constant in our bound analysis algorithm.