
\subsubsection{Loop Bound}
There are two methods for computing the loop bound, $BD(\rprog', c)$ for every sub program $\rprog'$ in $c$'s refined program $\rprog$.

Based only on the estimated ranking function from Section~\ref{sec:rank}, we can compute a loose $BD(\rprog', c)$ for each $\rprog'$
using the $\absclr(\absevent, c)$ as follows.
\begin{equation}
  \label{eq:absBD}
  BD(\rprog, c) = \min\left\{ \absclr(\absevent, c) \middle\vert \absevent \in \rprog \right\}.
\end{equation}
It is accurate only for simple loop, but not for multipath loops and the nested loops.
For example in Example~\ref{ex:relatedNestedWhileOdd-overview},
it computes $BD(\rprog_1^1) = n$ and $BD(\rprog_1^2) = n $ for the two interleaving pattern of loop $L_1$.
% The bounds for $\rprog_1^1$ and $\rprog_1^2$ are both $n$ while 
But both of their iteration bounds are expected to be $\lfloor\frac{m}{4}\rfloor$.
The inaccuracy is resulted by the nature of the path-insensitivity in the ranking function invariant estimation in Definition~\ref{def:ranking_bound}. 

We provide a new computation approach over the refined program.
It uses the estimated ranking function invariant and combines with the idea of progress invariant from~\cite{GulwaniJK09}.
We first compute three abstract states for each ranking function in different sub program of a refined program as below.
% Then we these precise abstract state, and estimate the loop bound path sensitively.
\begin{defn}[Rank Abstract States Computation]
  \label{def:alg-absstate}
  Given a program $c$ with its refined program $\rprog_c$ and a sub-program $\rprog$ in $\rprog_c$,
  we compute three abstract states, $\rfinit(\rprog, c)$, $\rffinal(\rprog, c)$ and $\rfnext(\rprog, c)$  for the ranking functions on this sub program as follows.
 \begin{itemize}
  \item 
  We first compute the initial execution point and continuation execution points of $\rprog$ denoted by
  $\absinit(\rprog)$
  and 
  $\absfinal(\rprog)$ using standard control flow method.
  \item The \emph{Initial State}, 
  $\rfinit(\rprog, c)$ is a set of equations $x = e$, where $e \in \scexpr(c)$ is a
  symbolic expression describing the initial value of $x$ before executing $\rprog$.
  Each $x$ is the ranking function of a simple transition path $\tpath$ in this program. 
  It contains the initial value for every ranking function of the simple transition path $\tpath$ in this program, 
  $\rfinit(\rprog, c) \triangleq $
  {\small
  \[
   \bigcup_{x \in \left\{ \locbound(\absevent, c) | \tpath \in \rprog \land \absevent \in \tpath \right\} }
   \left \{ 
   x = \arg\max_{l_1}\left\{
     \varinvar(y, c) + v ~\middle\vert~ 
     \begin{array}{l} 
       (l_1, x' \leq y + v, l_2) \in \reset(x, c) 
       \\
     \land l_1 \leq \absinit(\rprog, c)
   \end{array}
   \right\}
   \right\}
   \]
 }
 $\rfinit(\tpath, c)$ can also be estimated by $\kw{INIT(c, 0, \absinit(\rprog))}$ in \cite{GulwaniJK09}. 
 %
 \item  The \emph{Final State}, $\rffinal(\rprog, c)$ is a conjunction of boolean expressions, which is the set of minimum values for the ranking functions
 after executing $\rprog$.
  % $\rffinal(\rprog, c) \triangleq $
 % \\
 {\small
\[
  \begin{array}{l} 
   \bigcup\limits_{x \in \left\{ \locbound(\absevent, c) | \tpath \in \rprog \land \absevent \in \tpath \right\} }
   \left \{ 
   x = \min\limits_{ \left\{ l_1 ~|~ l_1 \geq \absfinal(\rprog, c) \right\} }
   \max\left\{
     v ~\middle\vert~ 
     \left( (x = v) \land \bigwedge\limits_{b \in \kw{B}(\rprog, c)} \neg b \right) \neq \efalse
   \right\}
   \right\}
  \end{array}
  \]
    }
    $\kw{B}(\rprog, c)$ is the set of all the boolean constraints in $\rprog$.
 \item The \emph{Next State}, $\rfnext(\rprog, c) \in \scexpr(c)$ 
 computes for the ranking functions on $\rprog$ the amount that each of them is changed after the first execution of $\rprog$ and before the second execution. This quantity is only required for $\tpath$.
 {\small
 \[
   \begin{array}{l}
   \rfnext(\tpath, c) \triangleq 
   \\
   \bigcup\limits_{x \in \left\{ \locbound(\absevent, c) | \absevent \in \tpath \right\}}
   \left\{ x = \begin{array}{l}
  \sum\limits_{\absevent \in \inc(x, c) }
   \left\{ v ~\middle\vert~ \absevent = (l, x' \leq x + v, \_) \land l \in \tpath\right\}
   \\ \qquad 
   + \arg\max\limits_{l' }
      \left\{ \varinvar(y, c) + v ~\middle\vert~ (l, x' \leq y + v, l') \in \reset(x, c) \land l \in \tpath\right\}
      \\ \qquad 
     - \sum\limits_{ \absevent \in \dec(x, c) }\left\{ 
       v ~\middle\vert~ \absevent = (l, x' \leq x - v, \_) \land l \in \tpath 
       \right\}
     \end{array}
   \right\} 
   \end{array}
 \]
  }
\end{itemize}
\end{defn}
Now we compute $BD(\rprog, c)$ recursively by interactively computing another quantity, $\varGD(\rprog, c)$ as follows.
\begin{defn}[Loop Bound Computation]
\label{def:loopbound}
Given a program $c$ with its refined program $\rprog$ and a subprogram $\rprog' = \rprepeat(\rprog_l) \in \rprog$,
the \emph{Variable Gradient Decent}, 
 $\varGD(\rprog', c)$ is an invariant of the minimum amount decreased in one execution of $\rprog_l$ for the ranking functions in $\rprog$,
%  and recursively computes the loop bound, $BD(\rprog, c)$ in the meantime.
{\small
\[
  \varGD(\rprog', c) \triangleq
  \left\{
   \begin{array}{ll}
    BD(\rprog', c)  \times {\varGD(\rprog_l', c)} &  \rprog' = \rprepeat(\rprog_l') \\
    \varGD(\rprog_1, c) + \varGD(\rprog_2, c) & \rprog' = \rprog_1;\rprog_2 \\
    \min\left\{v  ~|~ x = v \in \rfnext(\tpath, c) \right\}   & \rprog' = \tpath, 
    \end{array}
  \right.
 \]
 which is interactively computed together with $BD(\rprepeat(\rprog_l), c) \triangleq$
 \[
  % BD(\rprepeat(\rprog_l), c) =
  \left\{ 
    \begin{array}{ll}
      \max\limits_{x \in \left\{ \locbound(\absevent, c) | \absevent \in \tpath \right\}} 
      \Big\{ \highlight{\frac{a - b}{\varGD(\tpath, c)}}  &  \rprog_l = \tpath
      \\ \qquad 
      ~\vert~
      x = a \in \rfinit(\tpath, c)
      \land x = b \in \rffinal(\tpath, c)
      \Big\} 
      \\
      \max\limits_{x \in \left\{ \locbound(\absevent, c) | \absevent \in \tpath \right\}} 
      \Big\{ \highlight{\frac{\min\{ a, a - \varGD(\rprog_1, c) \} - b}{\varGD(\rprog_1;\rprog_2, c)}}  
      &  \rprog_l = \rprog_1;\rprog_2
      \\ \qquad 
      ~\vert~
      x = a \in \rfinit(\rprog_1, c)
      % \\ \qquad 
      \land x = b \in \rffinal(\rprog_2;\rprog_2, c)
      \Big\}   \\
      0  &  o.w.
    \end{array} 
    \right.
\]
}
\end{defn}
% This approach computes a sound loop bound for subprogram in a refined program formally in \highlight{Appendix~\ref{apdx:loopbound-sound}}.
In Example~\ref{ex:relatedNestedWhileOdd-overview}, we first compute $\rfinit = \{k = n - m\}$, $\rffinal = \{k = 0\}$ and $\rfnext = 1$ for subprogram $\rprepeat(\tpath_3)$ and get $BD(\rprepeat(\tpath_3)) = n - m$ tighter than $n$ by Eq.~\ref{eq:absBD}.
For the first iteration pattern $\rprog_1^1$ in Figure~\ref{fig:relatedNestedWhileOdd-overview}(b), we compute 
$\rfinit = \{k = n - m, i = m - 1\}$, $\rffinal = \{k = 0, i = 0\}$, $\varGD(\rprog_1^1) = 4$, and get $BD(\rprog_1^1) = \lfloor \frac{m}{4} \rfloor $ as expected.

Using the $BD$ computed by our new approach, we compute the local \emph{path reachability-bound} for
each $\tpath$ w.r.t. its \textbf{the innermost loop} as below.

\begin{defn}[Local Path Reachability-bound Computation]
    \label{def:pathlocalrb}
    Given program $c$ with its refined program $\rprog$ and a simple transition path $\tpath$ in this program, 
    let $l: \rprog_l = \kw{enclosed}(\rprog, \tpath)$ be a sub loop program in $\rprog$,
    then $\tpath$'s \emph{local reachability-bound} $\outinB(\rprog_l, \tpath, c)$ w.r.t. $l: \rprog_l$
    is computed inductively.
    {\small
    \[
      \left\{
    \begin{array}{ll}
       1  & \rprog = \tpath\\
      \highlight{0} & \rprog = \tpath' \neq \tpath\\
      \outinB(\rprog_1, \tpath, c) + \outinB(\rprog_2, \tpath, c) & \rprog = \rprog_1;\rprog_2 \\
      % \outinB(\rpchoose{\rprog_1, \ldots, \rprog_m }, \tpath) & \triangleq 
      % & 
      \max\left\{ \outinB(\rprog_1, \tpath, c), \ldots, \outinB(\rprog_m, \tpath, c) \right\} 
      & \rprog = \rpchoose{\rprog_1, \ldots, \rprog_m } \\
      % \outinB(\rprepeat(\rprog'), \tpath) & \triangleq 
      % & 
      BD(\rprepeat(\rprog'), c) \times \outinB(\rprog', \tpath, c) & \rprog = \rprepeat(\rprog')
    \end{array}
    \right.
    \]
    }
  \end{defn}
Soundness of the \emph{path local reachability-bound} is in \highlight{Appendix~\ref{apdx:pathlocalrb-sound}}.

  For the program in the first interleaving pattern $\rprog_1^1$ in Example~\ref{ex:relatedNestedWhileOdd-overview}, $\rprog_1^1$ is the innermost loop for $\tpath_1$, $\tpath_2$ and $\tpath_4$, 
  so compute $\outinB(\rprog_1^1, \tpath_1, c) = BD(\rprog_1^1, c) \times \outinB(\tpath_1; 4:\rprepeat(\tpath_3); \tpath_2; \tpath_4, \tpath_1, c)
  = BD(\rprog_1^1, c) \times (1 + 0) = \lfloor \frac{m}{4} \rfloor $ and the same for $\tpath_2$ and $\tpath_4$.

  Notice here, we can compute a loose $\psRB$ just using $\outinB(\rprog, \tpath, c)$. By replacing the restriction, $l: \rprog_l = \kw{enclosed}(\rprog, \tpath, c)$ in Definition~\ref{def:pathlocalrb} with $\rprog$, $\outinB(\rprog, \tpath, c)$ computes global \emph{path reachability-bound} loosely.
Then we can compute the $\psRB$ for every program point $l \in \lvar(c)$ by replacing the equation in Definition~\ref{def:point_psrb} with the following one,
\begin{equation}
  \label{eq:psrb-sub}
  \psRB(l, c) = 
  \sum
  \left\{ \outinB(\rprog, \tpath, c) ~\vert~ \tpath \in \rprog \land 
  l \in \tpath \right\}.
\end{equation}
It computes
$\outinB(\rprog, \tpath_3, c) = \frac{m}{4} \times (n - m)$ in Example~\ref{ex:relatedNestedWhileOdd-overview}.
It is loose because the Eq.~\ref{eq:psrb-sub} assumes the loop $L_4$ is reached in every iteration of the outer loop $L_1$. In this sense, $\psRB(4, c) = \frac{m}{4} \times (n - m)$ is loose as well.
While the \emph{loop reachability-bound} in the next section can help to compute the tighter \emph{reachability-bound}.
